Global patterns of forest autotrophic carbon fluxes

### 2020-02-17 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

Of the climate variables tested, annual wet days, aridity, cloud cover, mean diurnal temperature range, precipitation seasonality, maximum vapour pressure deficit and water stress months were poor or non-significant explainers of variation in FACF, explaining less than 20% of the variation in each of the carbon fluxes.

>>>>

Of the climate variables tested, annual wet days, aridity, cloud cover, precipitation seasonality, maximum vapour pressure deficit and water stress months were poor or non-significant explainers of variation in FACF, explaining less than 20% of the variation in each of the carbon fluxes.
